
---
title: "Music Insights"
author: "Chuck Franklin"
output:
  html_document:
    df_print: paged
---

Firt we need tidyverse to handle data importing and wrangling

```{r}
install.packages("tidyverse", repos="http://cran.us.r-project.org")
library("tidyverse")
```

```{r}
survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

Ignore these next two things (just testing out functions)
```{r}
nrow(survey)
colnames(survey)

```

We need to clean some data frame column names.
```{r}
colnames(survey)[colnames(survey)=="Timestamp"] <- "time_submitted"
colnames(survey)[colnames(survey)=="First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"
colnames(survey)[colnames(survey)=="What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey)=="Sex"] <- "sex"
colnames(survey)[colnames(survey)=="Major"] <- "academic_major"
colnames(survey)[colnames(survey)=="Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey)=="Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey)=="Which musical instruments/talents do you play? (Select all that apply)"] <- "instrument_list"
colnames(survey)[colnames(survey)=="Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey)=="Song"] <- "favorite_song"
colnames(survey)[colnames(survey)=="Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"

colnames(survey)
```

Now we should load some useful libraries.
```{r}
library("dplyr")
library("tidyr")
```

Let's create a "Person" table to include all of the respondents in the survey.
```{r}
Person <- tibble(time_submitted = survey$time_submitted, pseudonym_generator = survey$pseudonym_generator, pseudonym = survey$pseudonym, sex = survey$sex, academic_major = survey$academic_major, academic_level = survey$academic_level, year_born = survey$year_born)
```

Then, we can make a table for the favorite songs submitted.
```{r}
Favorite_song <- tibble(pseudonym = survey$pseudonym, artist = survey$favorite_song_artist, song = survey$favorite_song, link = survey$favorite_song_link)
```

The date/time needs to be more parseable.
```{r}
survey$time_submitted <- as.POSIXlt(parse_datetime(survey$time_submitted, "%m/%d/%y %H:%M"))
survey$time_submitted[1]$min
```

We need to convert the categorical data to factors.
```{r}
Person$academic_level <- as.factor(Person$academic_level)
levels(Person$academic_level)

Person$academic_major <- as.factor(Person$academic_major)
levels(Person$academic_major)

levels(Person$academic_major)[levels(Person$academic_major)=="Computer information systems"] <- "Computer Information Systems"

levels(Person$academic_major)
```

Now, we're going to create a new table called "Ratings," which will contain the users' pseudonyms, the song artists/titles, and the users' ratings of them.  This will be made up of data from the "preferences" data set, and will be put together using the "gather" function.
```{r}
Ratings <- gather(preferences, "artist_song", "rating", 3:45)
Ratings = select(Ratings, -1)
colnames(Ratings)[colnames(Ratings)=="What was your pseudonym?"] <- "pseudonym"
Ratings$pseudonym <- as.factor(Ratings$pseudonym)
Ratings$artist_song <- as.factor(Ratings$artist_song)
head(Ratings)
```